Negative and Fractional Types

### 2012-06-26 rational_ext.tex

We review our reversible language {{Pi}}: the presentation in this
section differs from the one in our previous paper~\cite{infeffects} in two
aspects. First, we add the empty type {{0}} which is necessary to express the
additive duality. Second, instead of explaining evaluation using a natural
semantics, we give a small-step operational semantics that is more
appropriate for the connections with continuations explored in this paper.

>>>>

We review our reversible language {{Pi}}: the presentation in this
section differs from the one in~\cite{infeffects} in two technical
aspects. First, we add the empty type {{0}} which is necessary to express the
additive duality. Second, instead of explaining evaluation using a natural
semantics, we give a small-step operational semantics that is more
appropriate for later parts of this paper.

There is also a notable shift in emphasis.  The terms of {{Pi}} are not
classical values and functions; rather, the terms are isomorphism 
witnesses.  In other words, the terms of {{Pi}} are proofs that certain
``shapes of values'' are isomorphic.  And, in classical Curry-Howard
fashion, our operational semantics shows how these proofs can be
directly interpreted as actions on ordinary values which effect this
shape transformation.

Of course, ``shapes of values'' are very familiar already: they are usually
called \emph{types}.  But usually one designs a type system as a method
of classifying terms, with the eventual purpose to show that certain
properties of well-typed terms hold, such as safety.  Our eventual goal
is different: we start from a type system, and are striving to discover
a term language which naturally inhabits these types, along with an
appropriate operational semantics.

Generally, such an approach would be rather vacuous.  What makes this
pursuit different is that ... (will continue from here -- Jacques)
